---
title: "README"
author: "Jay Zhang"
date: "5/3/2019"
output: github_document
---

```{r , echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      fig.path = "README-")
```

## Overview

`"binomial"` is a package that help you compute important parameters in binomial distribution and visualize the binomial distribution.

* `bin_choose` compute the combination of k successes in n trials
* `bin_probability` compute the probability of k successes in n trials
* `bin_distribution` display the binomial distribution with n trials and p probability
* `bin_cumulative` display the binomial cumulative distribution with n trials and p probability

## Movitation

The package has been developed to help compute binomial numbers and visualize the binomial distribution

##Installtion

```{r}
# install "cointoss" (without vignettes)
#devtools::install_github("stat133-sp19/hw-stat133-Jay1995712")

# install "cointoss" (with vignettes)
#devtools::install_github("stat133-sp19/hw-stat133-Jay1995712", build_vignettes=T)
```

