---
title: "Getting started with binomial package"
author: "Jay Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with binomial package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## binomial package

The package `"binomial"` contains tools to help you calculate some important paramaters such mean, variance, mode in binomial distribution, It also provides tools to help you visualize the binomial processes.

## function of  important measures in binomial

The functions to compute mean, variance, mode, skewness and kurtosis.
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

## function to compute possible combination 

The first input should be trials and the second input is successes.
```{r}
bin_choose(5,2)
```

## function to compute the probability

The first input should be the number of successes, the second input is trials and the third input should be the probability.
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

## binomial distribution and visualization

The `bin_distribution` function will create a table of binomial distribution for all the possible number of successes.
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

After you created the object/table, you can use `plot` to visualize the binomial distribution. It will display a hisgram with successes on x-axis and probability on y-axis.
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5) 
plot(dis1)
```

## binomial cumulative distribution

The `bin_cumulative` function will create a table of binomial cumulative distribution. The table is similar to the table of binomial distribution but with an additional column for cumulative probability.
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

After you create the data frame/table, you can use `plot` to visualize the binomial cumulative distribution in a scatterplot.
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5) 
plot(dis2)
```

## binomial variable 

The `bin_variable` will display the binomial variables of trials and successes.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3) 
bin1
```

You also can use `summary` to get additional parameters.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3) 
binsum1 <- summary(bin1)
binsum1
```

